#1. Loading and preprocessing the data
dat<- read.csv("activity.csv", header = TRUE, colClasses = c("numeric", "Date", "numeric")
##2. Process/transform the data (if necessary) into a format suitable for your analysis
```{r}
dat$interval <- strptime(gsub("([0-9]{1,2})([0-9]{2})", "\\1:\\2", dat$interval), format='%H:%M')
```
#3. What is mean total number of steps taken per day?
## Calculate the total number of steps taken per day
```{r}
library(ggplot2)
steps<- tapply (dat$steps, dat$date, sum, na.rm =TRUE)
```
##Calculate the total number of steps taken per day
```{r}
qplot(steps, xlab='Total steps per day', ylab='Frequency using binwith 500', binwidth=500)
```
##3. Calculate and report the mean and median total number of steps taken per day
```{r}
mean_steps <- mean(steps)
median_steps <- median(steps)
mean_steps
median_steps

```
#What is the average daily activity pattern?
##Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r}
library(dyplr)
actInterval <- dat %>% group_by(interval) %>% summarise(meanSteps = mean(steps,           na.rm = TRUE))
head(actInterval)

p <- ggplot(data = dat, mapping = aes(x = interval, y = meanSteps)) + 
    geom_line() + scale_x_continuous("Day Interval", breaks = seq(min(actInterval$interval), 
                                                                  max(actInterval$interval), 100)) + scale_y_continuous("Average Number of Steps") + 
    ggtitle("Average Number of Steps Taken by Interval")
p2
```

#Imputing missing values
##1. Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with NA\
```{r}
missingV <- is.na(dat$steps)


```
##Devise a strategy for filling in all of the missing values in the dataset. The strategy does not need to be sophisticated. For example, you could use the mean/median for that day, or the mean for that 5-minute interval, etc.
```{r}
fill.value <- function(steps, interval) {
    filled <- NA
    if (!is.na(steps))
        filled <- c(steps)
    else
        filled <- (averages[averages$interval==interval, "steps"])
    return(filled)
}
filled.data <- dat
filled.dat$steps <- mapply(fill.value, filled.data$steps, filled.data$interval)

```
#Are there differences in activity patterns between weekdays and weekends?
```{r}
total.steps <- tapply(filled.data$steps, filled.data$date, FUN=sum)
qplot(total.steps, binwidth=1000, xlab="total number of steps taken each day")
mean(total.steps)
median(total.steps)
```

#Are there differences in activity patterns between weekdays and weekends?
```{r}
weekday.or.weekend <- function(date) {
    day <- weekdays(date)
    if (day %in% c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday"))
        return("weekday")
    else if (day %in% c("Saturday", "Sunday"))
        return("weekend")
    else
        stop("invalid date")
}
#filled.data$date <- as.Date(filled.data$date)
#filled.data$day <- sapply(filled.data$date, FUN=weekday.or.weekend)
```